\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}


\title{Javascript}
\author{Sheet 3}
\date{}

\begin{document}
\maketitle

\begin{enumerate}
	\item  \textit{Celsius to Fahrenheit Conversion}. Write a JavaScript program that converts a temperature from Celsius to Fahrenheit. The formula to convert Celsius to Fahrenheit is: $F = (C \times 1.8) + 32$.
	\item \textit{Calculate the Average}. Write a program that calculates the average of a list of numbers.
	\item \textit{Determine the Largest Number}. Write a program that finds the largest number in a list of numbers.
	\item \textit{Check if a Number is Positive, Negative, or Zero}. Write a program that checks if a number is positive, negative, or zero.
	\item \textit{Calculate the Area of a Circle}. Write a program that calculates the area of a circle given its radius. The formula to calculate the area of a circle is: $A = \pi r^2$.
	\item \textit{Determine the Smallest Number}. Write a program that finds the smallest number in a list of numbers.
	\item \textit{Check if a Year is a Leap Year}. Write a program that checks if a year is a leap year. A leap year is divisible by 4, but not by 100, unless it is also divisible by 400.
	\item \textit{Convert Minutes to Hours and Minutes}. Write a JavaScript program that converts a duration from minutes to hours and minutes. For example, if the duration is 123 minutes, the program should output "2 hours, 3 minutes".
	\item \textit{Determine the Longest Word}. Write a program that finds the longest word in a sentence.
	\item \textit{Check if a Year is a Common Year}. Write a program that checks if a year is a common year. A common year is not a leap year.
	\item \textit{Calculate the Factorial}. Write a program that calculates the factorial of a number.
	\item \textit{Check if a Number is a Prime Number}. Write a program that checks if a number is a prime number.
	\item \textit{Count the Number of Vowels in a String}. Write a program that counts the number of vowels in a string.
	\item \textit{Check if a Number is a Perfect Number}. Write a program that checks if a number is a perfect number. A perfect number is a positive integer that is equal to the sum of its proper divisors (excluding itself).
	\item \textit{Calculate the GCD}. Write a program that calculates the greatest common divisor (GCD) of two numbers.
	\item \textit{Reverse a String}. Write a program that reverses a string.


\end{enumerate}


\end{document}